Union and intersection contracts are hard, actually

### 2021-07-26 paper.tex
Revision: side-effects (part 2)

This behavior indicates that union contracts introduce side-effects. The result
of \nickel{f 5} now depends on the previous execution and more specifically on
any prior call to \nickel{f}. This behavior of union contracts break the
property~\ref{eq:cbn-expansion} introduced in Section~\ref{sec:optimizations},
that is required to perform CSE-like optimizations in all generality. The
candidate example of Figure~\ref{fig:optimizations-let-floating-ex} in
Section~\ref{sec:optimizations} can't be optimized in general.

>>>>

This behavior indicates that union contracts introduce side-effects. The result
of \nickel{f 5} now depends on the previous execution and more specifically on
any prior call to \nickel{f}. This behavior of union contracts breaks
referential transparency, as well as the property~\ref{eq:cbn-expansion}
introduced in Section~\ref{sec:optimizations}, that is required to perform
CSE-like optimizations.
